---
title: "Higher Ed Enrollment Charts"
author: "Asha Muralidharan"
date: "2025-05-06"
output: html_document
---
##############################################################
# ACPS Student Success Audit - Higher Ed Enrollment Charts       
# Authors: Asha Muralidharan     
# GitHub: asha-ec                              
# Last revised: 2025-03-20
# Summary: A document that creates charts on Higher Ed Enrollment
#          for ACPS Student Success Audit
##############################################################

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##############################################################
# Call Libraries
##############################################################

library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)

ihe_allyears <- read_csv("../data/ACPS_higher_ed_enrollment_data_2008-24.csv")
```

##############################################################
# Racial Charts
##############################################################
```{r race}

ggplot() +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Race",
                                                student_group!="American Indian",
                                                student_group!="Native Hawaiian"),
            aes(x=short_year,y=four_ihe_pct,color="4 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Race",
                                                student_group!="American Indian",
                                                student_group!="Native Hawaiian"),
          aes(x=short_year,y=two_ihe_pct,color="2 Year")) +
  facet_wrap(~student_group)+
  theme_minimal()+
  scale_x_continuous(limits=c(11,23),breaks=seq(11,23,1))+
  scale_y_continuous(limits=c(0,100),breaks=seq(0,100,10),minor_breaks=seq(0,100,5))+
  labs(x="Cohort Year", y="Rate of Enrollment",
       title="Rate of Enrollment by Higher Ed Institution Type\nfor ACPS Students across Racial Categories")

```

##############################################################
# Student Membership Group Charts
##############################################################
```{r stu_membership, echo=FALSE}

ggplot() +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Disability"),
            aes(x=short_year,y=two_ihe_pct,color="2 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Disability"),
            aes(x=short_year,y=four_ihe_pct,color="4 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="English Learners"),
            aes(x=short_year,y=two_ihe_pct,color="2 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="English Learners"),
            aes(x=short_year,y=four_ihe_pct,color="4 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Economic Status"),
            aes(x=short_year,y=two_ihe_pct,color="2 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Economic Status"),
            aes(x=short_year,y=four_ihe_pct,color="4 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="All"),
            aes(x=short_year,y=two_ihe_pct,color="2 Year")) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="All"),
            aes(x=short_year,y=four_ihe_pct,color="4 Year"))+
  facet_wrap(~student_group)+
  theme_minimal()+
  scale_x_continuous(limits=c(11,23),breaks=seq(11,23,1))+
  scale_y_continuous(limits=c(0,100),breaks=seq(0,100,10),minor_breaks=seq(0,100,5))+
  labs(x="Cohort Year", y="Rate of Enrollment in Higher Ed Institution", 
       title="ACPS Rates of Postsecondary Enrollment by Student Group over Time: 2011-2024")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
