---
title: "Higher Ed Enrollment Charts"
author: "Asha Muralidharan"
date: "2025-05-06"
output: html_document
---
##############################################################
# ACPS Student Success Audit - Higher Ed Enrollment Charts       
# Authors: Asha Muralidharan     
# GitHub: asha-ec                              
# Last revised: 2025-03-20
# Summary: A document that creates charts on Higher Ed Enrollment
#          for ACPS Student Success Audit
##############################################################

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##############################################################
# Call Libraries
##############################################################

library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)

ihe_allyears <- read_csv("../data/ACPS_higher_ed_enrollment_data_2008-24.csv")
```

##############################################################
# Racial Charts
##############################################################
```{r race}


ggplot() +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Race",
                                                student_group!="American Indian",
                                                student_group!="Native Hawaiian"),
            aes(x=year,y=four_ihe_pct,color="4 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Race",
                                                student_group!="American Indian",
                                                student_group!="Native Hawaiian"),
          aes(x=year,y=two_ihe_pct,color="2 Year Institution",group=1)) +
  facet_wrap(~student_group)+
  theme_minimal()+
  scale_y_continuous(limits=c(0,100),breaks=seq(0,100,10),minor_breaks=seq(0,100,5))+
  labs(x="Cohort Year", y="Rate of Enrollment",
       title="Rate of Enrollment by Higher Ed Institution Type\nfor ACPS Students across Racial Categories")+
  geom_text(size = 5, hjust=0.5, vjust=-1, color="black") + 
  scale_color_manual(values = c("#f8be3d","#0c9ed9")) + 
  theme(legend.title=element_blank(), 
        legend.position = "top", 
        legend.text = element_text(size = 12, hjust=.5), 
        axis.text.x = element_text(color = "black", size = 10, angle = 45, hjust = 1), 
        axis.ticks = element_blank(), 
        plot.title.position= "plot", 
        plot.caption.position = "plot", 
        axis.text.y = element_text(size = 10), 
        text = element_text(size = 12, family="sans"), 
        plot.title = element_text(size = 16, hjust=.65), 
        plot.caption = element_text(size = 14))

```

##############################################################
# Student Membership Group Charts
##############################################################
```{r stu_membership, echo=FALSE}

ggplot() +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Disability"),
            aes(x=year,y=two_ihe_pct,color="2 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Disability"),
            aes(x=year,y=four_ihe_pct,color="4 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="English Learners"),
            aes(x=year,y=two_ihe_pct,color="2 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="English Learners"),
            aes(x=year,y=four_ihe_pct,color="4 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Economic Status"),
            aes(x=year,y=two_ihe_pct,color="2 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="Economic Status"),
            aes(x=year,y=four_ihe_pct,color="4 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="All"),
            aes(x=year,y=two_ihe_pct,color="2 Year Institution",group=1)) +
  geom_line(data=ihe_allyears %>% dplyr::filter(data_level=="All"),
            aes(x=year,y=four_ihe_pct,color="4 Year Institution",group=1))+
  facet_wrap(~student_group)+
  theme_minimal()+
  scale_y_continuous(limits=c(0,100),breaks=seq(0,100,10),minor_breaks=seq(0,100,5))+
  labs(x="Cohort Year", y="Rate of Enrollment", 
       title="ACPS Rates of Postsecondary Enrollment\nby Student Group over Time: 2011-2024")+
  geom_text(size = 5, hjust=0.5, vjust=-1, color="black") + 
  scale_color_manual(values = c("#f8be3d","#0c9ed9")) + 
  theme(legend.title=element_blank(), 
        legend.position = "top", 
        legend.text = element_text(size = 12, hjust=.5), 
        axis.text.x = element_text(color = "black", size = 10, angle = 45, hjust = 1), 
        axis.ticks = element_blank(), 
        plot.title.position= "plot", 
        plot.caption.position = "plot", 
        axis.text.y = element_text(size = 10), 
        text = element_text(size = 12, family="sans"), 
        plot.title = element_text(size = 16, hjust=.65), 
        plot.caption = element_text(size = 14))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
